Learning STRIPS action models with classical planning

### 2017-10-28 doc/icaps-18/strips-learning.tex
Added static predicates results to the paper

\begin{table}[hbt!]
\begin{footnotesize}
	\begin{center}
		\begin{tabular}{l|l|l|l|l|l|l|}
			 & \multicolumn{2}{|c|}{\bf Pre} & \multicolumn{2}{|c|}{\bf Add} & \multicolumn{2}{|c|}{\bf Del}  \\ \cline{2-7}			
			  & \multicolumn{1}{|c|}{\bf P} & \multicolumn{1}{|c|}{\bf R} & \multicolumn{1}{|c|}{\bf P} & \multicolumn{1}{|c|}{\bf R} & \multicolumn{1}{|c|}{\bf P} & \multicolumn{1}{|c|}{\bf R} \\
			\hline
			Blocks & 1.0 & 1.0 & 1.0 & 1.0 & 1.0 & 1.0 \\
			Driverlog & 1.0 & 0.4 & 0.6 & 0.8 & 1.0 & 0.8 \\
			Ferry & 0.8 & 0.5 & 1.0 & 1.0 & 1.0 & 1.0 \\
			Floortile & 0.5 & 0.6 & 0.9 & 0.8 & 1.0 & 0.9 \\
			Gripper & 1.0 & 0.6 & 1.0 & 1.0 & 1.0 & 1.0 \\
			Miconic & 0.7 & 0.3 & 1.0 & 0.7 & 0.7 & 1.0 \\
			Satellite & 0.6 & 0.2 & 1.0 & 1.0 & 1.0 & 0.75 \\
			Transport & 1.0 & 0.3 & 0.5 & 0.8 & 1.0 & 0.6 \\
			Visitall & 1.0 & 0.5 & 1.0 & 1.0 & 1.0 & 1.0 \\
			Zenotravel & 1.0 & 0.3 & 0.7 & 0.8 & 1.0 & 0.7
		\end{tabular}
	\end{center}
	\end{footnotesize}
\caption{\small The {\em precision} and {\em recall} values achieved by the learned models in the $\Lambda$ learning tasks exploiting the computed static predicates.}
\label{tab:results_plans_static}
\end{table}

\begin{table}[hbt!]
\begin{footnotesize}
	\begin{center}
		\begin{tabular}{l|c|c|c|}			
			Domain & Total time & Preprocess & Plan length  \\
			\hline
			Blocks & 0.04 & 0.00 & 72 \\
			Driverlog & 0.10 & 0.06 & 127 \\
			Ferry & 0.20 & 0.10 & 58 \\
			Floortile & 2.15 & 1.21 & 170 \\
			Gripper & 0.01 & 0.00 & 45 \\
			Miconic & 0.10 & 0.09 & 54 \\
			Satellite & 0.20 & 0.14 & 67 \\
			Transport & 0.20 & 0.18 & 60 \\
			Visitall & 0.43 & 0.39 & 37 \\
			Zenotravel & 2.78 & 2.76 & 70
		\end{tabular}
	\end{center}
        \end{footnotesize}
	\caption{\small Planning time, preprocessing time and Plan length exploiting the computed static predicates.}
	\label{tab:time_plans_static}	
\end{table}

>>>>

\begin{table}[hbt!]
\begin{footnotesize}
	\begin{center}
		\begin{tabular}{l|l|l|l|l|l|l|}
			 & \multicolumn{2}{|c|}{\bf Pre} & \multicolumn{2}{|c|}{\bf Add} & \multicolumn{2}{|c|}{\bf Del}  \\ \cline{2-7}			
			  & \multicolumn{1}{|c|}{\bf P} & \multicolumn{1}{|c|}{\bf R} & \multicolumn{1}{|c|}{\bf P} & \multicolumn{1}{|c|}{\bf R} & \multicolumn{1}{|c|}{\bf P} & \multicolumn{1}{|c|}{\bf R} \\
			\hline
			Blocks & 1.0 & 1.0 & 1.0 & 1.0 & 1.0 & 1.0 \\
			Driverlog & 1.0 & 0.5 & 0.8 & 0.9 & 1.0 & 0.7 \\
			Ferry & 0.8 & 0.6 & 1.0 & 1.0 & 1.0 & 1.0 \\
			Floortile & 0.7 & 0.8 & 0.9 & 0.8 & 1.0 & 0.9 \\
			Gripper & 1.0 & 0.7 & 1.0 & 1.0 & 1.0 & 1.0 \\
			Miconic & 0.9 & 0.8 & 1.0 & 0.8 & 0.8 & 1.0 \\
			Satellite & 0.8 & 0.8 & 0.8 & 1.0 & 1.0 & 0.8 \\
			Transport & 1.0 & 0.6 & 0.8 & 0.8 & 1.0 & 0.6 \\
			Visitall & 1.0 & 1.0 & 1.0 & 1.0 & 1.0 & 1.0 \\
			Zenotravel & 1.0 & 0.6 & 0.8 & 0.9 & 1.0 & 0.7
		\end{tabular}
	\end{center}
	\end{footnotesize}
\caption{\small The {\em precision} and {\em recall} values achieved by the learned models in the $\Lambda$ learning tasks exploiting the computed static predicates.}
\label{tab:results_plans_static}
\end{table}

\begin{table}[hbt!]
\begin{footnotesize}
	\begin{center}
		\begin{tabular}{l|c|c|c|}			
			Domain & Total time & Preprocess & Plan length  \\
			\hline
			Blocks & 0.03 & 0.00 & 72 \\
			Driverlog & 0.12 & 0.07 & 102 \\
			Ferry & 0.25 & 0.15 & 58 \\
			Floortile & 0.73 & 0.43 & 80 \\
			Gripper & 0.01 & 0.00 & 45 \\
			Miconic & 0.06 & 0.04 & 40 \\
			Satellite & 0.18 & 0.12 & 60 \\
			Transport & 0.18 & 0.18 & 44 \\
			Visitall & 0.43 & 0.42 & 33 \\
			Zenotravel & 0.26 & 0.25 & 53
		\end{tabular}
	\end{center}
        \end{footnotesize}
	\caption{\small Planning time, preprocessing time and Plan length exploiting the computed static predicates.}
	\label{tab:time_plans_static}	
\end{table}
